Interval-based Robust Control of Linear Systems with Generic Costs

### 2020-05-25 main.tex
Last remark from Denis

The motivation behind this work is to enable the development of Reinforcement Learning solutions for industrial applications, when it has been mainly limited to simulated games so far. In particular, many industries already rely on non-adaptive control systems and could benefit from an increased efficiency, including Oil and Gas, robotics for industrial automation, Data Center cooling, etc. But more often than not, safety-critical constraints bar the use of exploration, and industrials are reluctant to turn to learning-based methods that lack accountability. This work addresses these concerns by focusing on risk-averse decisions and by providing worst-case guarantees. Note however that these guarantees are only as good as the validity of the underlying hypotheses, and \Cref{assumpt:structure} in particular should be submitted to a comprehensive validation procedure; otherwise, decisions formed on a wrong basis could easily lead to dramatic consequences in such critical settings.
Beyond industrial perspectives, this work could be of general interest for risk-averse decision-making. For instance, parametrized epidemiological models have been used to represent the propagation of Covid\nobreakdash-19 and study the impact of several lockdown policies. These model parameters are estimated from observational data and corresponding confidence intervals are often available, but rarely used in the decision-making loop. In contrast, our approach would enable evaluating and optimising the worst-case outcome of such public policies.

>>>>

The motivation behind this work is to enable the development of Reinforcement Learning solutions for industrial applications, when it has been mainly limited to simulated games so far. In particular, many industries already rely on non-adaptive control systems and could benefit from an increased efficiency, including Oil and Gas, robotics for industrial automation, Data Center cooling, etc. But more often than not, safety-critical constraints proscribe the use of exploration, and industrials are reluctant to turn to learning-based methods that lack accountability. This work addresses these concerns by focusing on risk-averse decisions and by providing worst-case guarantees. Note however that these guarantees are only as good as the validity of the underlying hypotheses, and \Cref{assumpt:structure} in particular should be submitted to a comprehensive validation procedure; otherwise, decisions formed on a wrong basis could easily lead to dramatic consequences in such critical settings.
Beyond industrial perspectives, this work could be of general interest for risk-averse decision-making. For instance, parametrized epidemiological models have been used to represent the propagation of Covid\nobreakdash-19 and study the impact of several lockdown policies. These model parameters are estimated from observational data and corresponding confidence intervals are often available, but rarely used in the decision-making loop. In contrast, our approach would enable evaluating and optimising the worst-case outcome of such public policies.
